Requiem for a Balanced Life: Analysis of My Behavioural Patterns as a PhD Student

### 2023-04-05 outputs/paper/timesheet_analysis.qmd
correct typo & update graph based on Cindy's input

# Piecharts: https://r-charts.com/part-whole/pie-chart-ggplot2/
cleaned_time_sheet |>
  group_by(type) |>
  summarize(effort = sum(effort_hours)) |>
  mutate(effort_pct = effort / sum(effort)) |>
  ggplot(aes(x = "", y = effort_pct, fill = fct_rev(type))) +
  geom_col(color = "black") +
  geom_label(aes(label = round(effort, 0)),
             position = position_stack(vjust = 0.5),
             size = 3,
             show.legend = FALSE) +
  coord_polar(theta = "y") +
  labs(
    y = "Effort (Hours)",
    fill = "Type"
  ) +
  scale_fill_viridis(discrete = TRUE) #colorblind-friendly palette
```

>>>>

# Piecharts: https://r-charts.com/part-whole/pie-chart-ggplot2/
cleaned_time_sheet |>
  group_by(type) |>
  summarize(effort = sum(effort_hours)) |>
  mutate(effort_pct = effort / sum(effort)) |>
  ggplot(aes(x = "", y = effort_pct, fill = fct_rev(type))) +
  geom_col(color = "black") +
  geom_label(aes(label = round(effort, 0)),
             position = position_stack(vjust = 0.5),
             fill = "white",
             size = 3,
             show.legend = FALSE) +
  coord_polar(theta = "y") +
  labs(
    y = "Effort (Hours)",
    fill = "Type"
  ) +
  scale_fill_viridis(discrete = TRUE) #colorblind-friendly palette
```
